Forecasting Gamma-ray Bursts using Gravitational Waves

### 2018-03-16 Paper/Manuscript.tex
Intro

Given the sensitivities of IFOs to date, efforts have thus far mostly focused on reducing the latency of EM follow-ups, 
i.e., the lag time between the merger and the alerting of the EM observatories. 
LIGO-Virgo science runs in 2009-2010 yielded a latency of $\sim 30\,$minutes \cite{Abbott:2011ys} (no detections).
In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd} 
with an additional $\sim 10$ hours to locate the optical transient now designated as AT 2017gfo.

Here, we turn this around and focus instead on how much advance warning times near-future ground-based GW detectors can provide us.
Ref.~\cite{Cannon:2011vi} took up this challenge algorithmically and focused on developing inexpensive methods to detect inspiral
signals in GW data to provide early-warning triggers \emph{before} the merger.

@@

 already attemps some forecast, but they focus on the search algorithm side of things

>>>>

Given the sensitivities of IFOs to date, efforts have thus far mostly focused on reducing the latency of EM follow-ups, 
i.e., the lag time between the merger and the alerting of the EM observatories. 
LIGO-Virgo science runs in 2009-2010 yielded a latency of $\sim 30\,$minutes \cite{Abbott:2011ys} (no detections).
In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd}.
It then took an additional $\sim 10$ hours to locate the optical transient designated AT 2017gfo.

Here, we turn this around and focus instead on how much advance warning times near-future ground-based GW detectors can provide us.
Ref.~\cite{Cannon:2011vi} considered this by focussing on developing computationally inexpensive methods to detect inspiral
signals in GW data to provide early-warning triggers \emph{before} the merger.
We instead focus on the forecasting capabilities of the ground-based IFOs at their full design sensitivity.
To this end, we consider the $\sim 2020$-design sensitivity of the Advanced-LIGO-Virgo (ALV) network composed of three IFOs and the $\sim 2030$-design
sensitivity of Einstein Telescope.

@@

Sec.~ blah blah, Sec.~ does so and so, results are presented in Sec.~
